---
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# roomba
[![Travis build status](https://travis-ci.com/ropenscilabs/roomba.svg?branch=master)](https://travis-ci.com/ropenscilabs/roomba)

This is a package to transform large, multi-nested lists into a more
user-friendly format (i.e. a `tibble`) in `R`. The initial focus is on making
processing of return values from `jsonlite::fromJSON()` queries more seamless,
but ideally this package should be useful for deeply-nested lists from an array
of sources.

*Key features:*

* `roomba()` searches deeply-nested list for names specified in
  `cols` (a character vector) and returns a `tibble` with the
  associated column titles. Nothing further about nesting hierarchy or
  depth need be specified.
* Handles empty values gracefully by substituting `NULL` values with 
 `NA` or user-specified value in `.default`, or truncates lists appropriately. 
 * Option to `.keep` `any` or `all` data from the columns supplied

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ropenscilabs/roomba")
```

## Example

Say we have some JSON from a pesky API.

```{r example}
library(roomba)

json <- '
  {
    "stuff": {
      "buried": {
        "deep": [
        {
          "location": "here",
          "name": "Amanda",
          "super_power": "flight",
          "more_nested_stuff": 4
        },
        {
          "location": "here",
          "name": "Christine",
          "super_power": "water-breathing"
        },
        {
          "location": "here",
          "name": "Isabella",
          "super_power": "teleportation"
        }
        ],
        "alsodeep": 2342423234,
        "deeper": {
          "foo": [
          {
            "location": "not here",
            "name": "Jim"
          },
          {
            "location": "here",
            "name": "Isabella Velasquez",
            "secret_power": "shape-shifting"
          },
          {
            "location": "here",
            "name": "Christine Stawitz",
            "secret_power": "shape-shifting"
          },
          {
             "location": "here",
             "name": "Laura",
             "super_power": "git"
          }
          ]
        }
      }
    }
  }'
```

The JSON becomes a nested R list

```{r}
super_data <- json %>% 
  jsonlite::fromJSON(simplifyVector = FALSE)
```

Which we can pull data into the columns we want with `roomba`.

```{r}
super_data %>%
  roomba(cols = c("name", "super_power", "location"), keep = any)
```


Let's try with a real-world Twitter example.

```{r}
twitter_data[[1]]
```


```{r}
roomba(twitter_data, c("created_at", "name"))
```



