---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# roomba

This is a package to transform large, multi-nested lists into a more
user-friendly format (i.e. a `tibble`) in `R`. The initial focus is on making
processing of return values from `jsonlite::fromJSON()` queries more seamless,
but ideally this package should be useful for deeply-nested lists from an array
of sources.

Key features of the package:
* `roomba(rows = , cols = )` searches deeply-nested list for names specified in
  `rows` or `cols` arguments (string vectors) and returns a `tibble` with the
  associated row or column titles. Nothing further about nesting hierarchy or
  depth need be specified.
* handles empty values gracefully via `replace_nulls()` function that
  substitutes `NULL` values with `NA` or user-specified value, or truncates
  lists appropriately. The goal of roomba is to tidy recursive lists.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ropenscilabs/roomba")
```
## Example

```{r example}
x <- data(example_data)

#Existing example
x %>%
  dfs_idx(~ .x$goodstuff == "here") %>%
  purrr:::map_dfr(~ x[[.x]])

#Eventual roomba syntax
x %>%
  roomba(rows=c('goodstuff'),
         cols = c('name','secret_power',
                  'more_nested_stuff'))
```
