
---
slug: "roomba"
title: A package for tidying nested lists
package_version: 0.0.1
authors:
  - name: Amanda Dobbyn
    url: https://github.com/aedobbyn
  - name: Jim Hester
        url: https://github.com/jimhester
  - name: Laura DeCicco
          url: https://github.com/ldecicco-USGS
  - name: Christine Stawitz
        url: https://github.com/cstawitz
  - name: Isabella Velasquez 
     url: https://github.com/ivelasq
date: 2018-06-18
categories: blog
topicid: 925
tags:
- r
- community
- software
- review
- onboarding
- package
---
Data == knowledge! Much of the data we use, whether it be from government repositories, social media, GitHub, or e-commerce sites comes from public-facing APIs. The quantity of data available is truly staggering, but munging JSON output into a format that is easily analyzable in R is an equally staggering undertaking. When JSON is turned into an R object, it usually becomes a deeply nested list riddled with missing values that is difficult to untangle into a tidy format. Moreover, every API presents its own challenges; code you've written to clean up data from GitHub isn't necessarily going to work on Twitter data, as each API spews data out in its own unique, headache-inducing nested list structure. To ease and generalize this process, [Amanda Dobbyn proposed](https://github.com/ropensci/unconf18/issues/24) an #unconf18 project for a general API response tidier! Welcome `roomba`, our first stab at easing the process of tidying nested lists!


`roomba` will eventually be able to walk nested lists in a variety of different structures from JSON output, replace  `NULL` or `.empty` values with `NA`s or a user-specified value, and return a `tibble` with names matching a user-specified list. Of course, in two days we haven't *fully* achieved this vision, but we're off to a promising start.


## The birth of roomba


It was clear Amanda was on to something good by the lively discussion in the [#runconf18](https://github.com/ropensci/unconf18/issues/24) issues repository leading up to the unconf. Thanks to input from Jenny Bryan, Jim Hester, Carl Boettinger, Scott Chamberlain, Bob Rudis, and Noam Ross, we had a lot of ideas to work with when the unconf began. Fortunately, Jim already had a function called `dfs_idx()` ([here](https://github.com/ropenscilabs/roomba/blob/master/R/dfs_idx.R)) written to perform depth-first searches of nested lists from the [GitNub GraphQL API](https://developer.github.com/v4/). With the core list-traversal code out of the way, we split our efforts between developing a usable interface, stockpiling `.JSON` files to test on, and developing a Shiny app.


## What's working
We've got the basic structure of `roomba` sorted out, and you should install it from GitHub to try out! Here are a few of the examples we've put together. 


  ```{r}
  #load twitter data example
  data(twitter_data)


#roomba-fy!
roomba(twitter_data, c("created_at", "name"))
```
And just the *first* element of the `twitter_data` list will show you that `roomba` has simplified this process quite a bit.
```{r}
twitter_data[[1]]
$`created_at`
[1] "Mon May 21 17:58:09 +0000 2018"


$id
[1] 9.98624e+17


$id_str
[1] "998623997397876743"


$text
[1] "Could a program like food stamps have a Cambridge Analytica moment? How do we allow for the innovation that data pl… https://t.co/7tVf1qmNmq"


$truncated
[1] TRUE


$entities
$entities$`hashtags`
list()


$entities$`symbols`
list()


$entities$`user_mentions`
list()


$entities$`urls`
$entities$`urls`[[1]]
$entities$`urls`[[1]]$`url`
[1] "https://t.co/7tVf1qmNmq"


$entities$`urls`[[1]]$expanded_url
[1] "https://twitter.com/i/web/status/998623997397876743"


$entities$`urls`[[1]]$display_url
[1] "twitter.com/i/web/status/9…"


$entities$`urls`[[1]]$indices
$entities$`urls`[[1]]$indices[[1]]
[1] 117


$entities$`urls`[[1]]$indices[[2]]
[1] 140










$source
[1] "<a href=\"https://about.twitter.com/products/tweetdeck\" rel=\"nofollow\">TweetDeck</a>"


$in_reply_to_status_id
NULL


$in_reply_to_status_id_str
NULL


$in_reply_to_user_id
NULL


$in_reply_to_user_id_str
NULL


$in_reply_to_screen_name
NULL


$user
$user$`id`
[1] 64482503


$user$id_str
[1] "64482503"


$user$name
[1] "Code for America"


$user$screen_name
[1] "codeforamerica"


$user$location
[1] "San Francisco, California"


$user$description
[1] "Government can work for the people, by the people, in the 21st century. Help us make it so."


$user$url
[1] "https://t.co/l9lokka0rJ"


$user$entities
$user$entities$`url`
$user$entities$`url`$`urls`
$user$entities$`url`$`urls`[[1]]
$user$entities$`url`$`urls`[[1]]$`url`
[1] "https://t.co/l9lokka0rJ"


$user$entities$`url`$`urls`[[1]]$expanded_url
[1] "http://codeforamerica.org"


$user$entities$`url`$`urls`[[1]]$display_url
[1] "codeforamerica.org"


$user$entities$`url`$`urls`[[1]]$indices
$user$entities$`url`$`urls`[[1]]$indices[[1]]
[1] 0


$user$entities$`url`$`urls`[[1]]$indices[[2]]
[1] 23










$user$entities$description
$user$entities$description$`urls`
list()






$user$`protected`
[1] FALSE


$user$followers_count
[1] 49202


$user$friends_count
[1] 1716


$user$listed_count
[1] 2659


$user$created_at
[1] "Mon Aug 10 18:59:29 +0000 2009"


$user$favourites_count
[1] 4490


$user$utc_offset
[1] -25200


$user$time_zone
[1] "Pacific Time (US & Canada)"


$user$geo_enabled
[1] TRUE


$user$verified
[1] TRUE


$user$statuses_count
[1] 15912


$user$lang
[1] "en"


$user$contributors_enabled
[1] FALSE


$user$is_translator
[1] FALSE


$user$is_translation_enabled
[1] FALSE


$user$profile_background_color
[1] "EBEBEB"


$user$profile_background_image_url
[1] "http://abs.twimg.com/images/themes/theme7/bg.gif"


$user$profile_background_image_url_https
[1] "https://abs.twimg.com/images/themes/theme7/bg.gif"


$user$profile_background_tile
[1] FALSE


$user$profile_image_url
[1] "http://pbs.twimg.com/profile_images/615534833645678592/iAO_Lytr_normal.jpg"


$user$profile_image_url_https
[1] "https://pbs.twimg.com/profile_images/615534833645678592/iAO_Lytr_normal.jpg"


$user$profile_banner_url
[1] "https://pbs.twimg.com/profile_banners/64482503/1497895952"


$user$profile_link_color
[1] "CF1B41"


$user$profile_sidebar_border_color
[1] "FFFFFF"


$user$profile_sidebar_fill_color
[1] "F3F3F3"


$user$profile_text_color
[1] "333333"


$user$profile_use_background_image
[1] FALSE


$user$has_extended_profile
[1] FALSE


$user$default_profile
[1] FALSE


$user$default_profile_image
[1] FALSE


$user$following
[1] TRUE


$user$follow_request_sent
[1] FALSE


$user$notifications
[1] FALSE


$user$translator_type
[1] "none"




$geo
NULL


$coordinates
NULL


$place
NULL


$contributors
NULL


$is_quote_status
[1] FALSE


$retweet_count
[1] 0


$favorite_count
[1] 0


$favorited
[1] FALSE


$retweeted
[1] FALSE


$possibly_sensitive
[1] FALSE


$possibly_sensitive_appealable
[1] FALSE


$lang
[1] "en"
```
We created a Shiny app too, which in its current state allows you to select a `.Rda` or `.JSON` file, pick two variables, and create a scatterplot of them.


Run the app like this:
```{r eval=FALSE}
shiny_roomba()
```
## What's not
Of course, in two days we weren’t able to build a magical one-size-fits-all solution to every API response data headache. Right now, the main barrier to usability is that both the `roomba()` function and `shiny_roomba()` app only work on sub-list items of the same length and same data type stored at the same depth. To illustrate on the `twitter_data`:
```{r}
#This doesn't work because "user" has data of different types and lengths
roomba(twitter_data, c("user"))
# A tibble: 1,007 x 1
   user      
   <list>    
 1 <int [1]> 
 2 <chr [1]> 
 3 <chr [1]> 
 4 <chr [1]> 
 5 <chr [1]> 
 6 <chr [1]> 
 7 <chr [1]> 
 8 <list [2]>
 9 <lgl [1]> 
10 <int [1]> 
# ... with 997 more rows


#This doesn't work because "name" and "retweet_count" are at different depths.
roomba(twitter_data, c("name","retweet_count"))
# A tibble: 0 x 0
```


In addition, we've got some features we want to add, such as handling a larger variety of column names (i.e. passing a string for a single column name, keeping all values even if they are all `NULL`). We would love your feedback on other things we can add!


## The team 

**Amanda Dobbyn**
Job: Data Scientist at Earlybird Software
Project contributions: initial GH issue, package name, wrapper for `dfs_idx()`

**Jim Hester**

**Christine Stawitz**
Job: Postdoctoral researcher at UW's School of Aquatic and Fishery Sciences
Project contributions: Shiny app, README and blog post writing

**Laura DeCicco**
Job: Data Scientist at U.S. Geological Survey
Project contributions: Fixing merge conflicts :)

**Isabella Velasquez**


<!--stackedit_data:
eyJoaXN0b3J5IjpbLTk1NzM5MzYxOCwtMTMyNDAxNTUxNiwzOT
c2NzQ3NjUsODI1NjMxNDk3LDc2NjI0ODQ1OSwxOTc2NTk0Mzk1
LDIwMjU3NzM5ODAsLTEzNjU5NTg4NjgsMTg0MDE1NDg4NiwxNz
gxMjUxMDcwXX0=
-->
